A Gentle Introduction to Structural Causal Models

### 2021-05-20 presentation_video.Rmd
independence assumption
toc

* Foundations of SCMs 
  * Assumptions 
  * Comparative Causal Tools 
  * Historical Development 
* Pearl's Causal Hierachy 
  * prediction 
  * intervention 
  * Counterfactuals 
  * Implications 
* Graphical Models 
  * Features 
  * Implications
* Causality and Time

@@

- Consists of system of equations 
- Assignment equation ':=' rather than regular equation '=' 
- is a nonparametric SEM 
- has functional form rather than using probabilities
- entails features from the PO framework and graphical representation 
- Exogenous factors are part of the model specification

@@

>>>>

* Foundations of SCMs 
  * Assumptions 
  * Comparative Causal Tools 
  * Historical Development 
* Pearl's Causal Hierachy 
  * Prediction 
  * Intervention 
  * Counterfactuals 
  * Implications 
* Graphical Models 
  * Features 
  * Implications
* Causality and Time

@@

- Consists of system of equations 
- Assignment equation ':=' rather than regular equation '=' 
- Nonparametric SEM 
- Functional form rather than using  conditional probabilities
- entails features from the PO framework and graphical representation 
- Exogenous factors are part of the model specification

@@

# Assumptions (4)

**Independence**

*Definition:*
